Future challenges for Research Software Engineering

### 2025-05-09 future_challenges_for_RSEng.tex
Convert introduction to running text

% Main part of your article
% =========================
\section{Introduction}
This opinion article stems from a Bof session at deRSE25 in Karlsruhe\cite{Goth2025EndRSEng}.
Therefore it stems from a discussion among the participants of this workshop and hence cannot claim that it represents the entire deRSE community.
Nevertheless we hope, that we succeeded in writing up something that
\begin{itemize}
\item is pleasant to read,
\item gives something to think about,
\item motivates engaging in work towards a better future.
\end{itemize}
In order to structure the discussion, we decided on an imaginable setting ten years from now.
In this world we will consider the dimensions of 
\begin{itemize}
\item Evolution of the term RSEs
\item The development of academic institutions
\item What will the impact of AI be to the work of RSEs?
\item How will academic education have transformed by then
\item Ethics and social considerations
\end{itemize}
In each aspect we will quickly summarise on what we want to have achieved by then, and what will be the challenges that arise from that.

>>>>

% Main part of your article
% =========================
\section{Introduction}

Research Software Engineering is currently an emerging field,
with an increasing integration in various aspects of research.
In this opinion paper, we try to imagine the state of our field
and community in the mid-term future, focusing on future challenges.
We present here the results of a workshop discussion at the
deRSE25 conference in Karlsruhe\cite{Goth2025EndRSEng}, without
claiming to represent the entire deRSE community.
Nevertheless, by disseminating the discussed ideas,
we aim to engage the community in imagining the future.
In the following sections, we consider the evolution of the RSE definition,
the development of RSE education,
the impact of automation and generative artificial intelligence in RSE work,
the emerging ethical considerations,
and the transformations expected in the research organizations.
We then attempt to make long-term predictions
and we conclude the paper with our wishes and recommendations.
